A Logical Solution of the Linearity Challenge

### 2025-12-03 paper/DeadlockFreedom.lagda.tex
restored DF

\begin{code}[hide]
open import Data.Sum
open import Data.Product using (_×_; _,_; ∃; ∃-syntax)
open import Data.Bool using (Bool; true; false; if_then_else_)
open import Data.List.Base using ([]; _∷_; [_])
open import Relation.Nullary using (¬_; contradiction)
open import Relation.Binary.PropositionalEquality using (refl)

@@

\begin{AgdaAlign}
\begin{code}[hide]
data Cut where
  cut :
    ∀{Γ Γ₁ Γ₂ A B} (d : Dual A B) (p : Γ ≃ Γ₁ + Γ₂)
    {P : Process (A ∷ Γ₁)} {Q : Process (B ∷ Γ₂)} →
    Cut (cut d p P Q)

data Link where
  link :
    ∀{Γ A B} (d : Dual A B) (p : Γ ≃ [ A ] + [ B ]) → Link (link d p)

data Input where
  fail :
    ∀{Γ Δ}
    (p : Γ ≃ [] + Δ) → Input (fail (split-l p))
\end{code}

\begin{code}
  wait : ∀{Γ Δ} (p : Γ ≃ [] + Δ) {P : Process Δ} → Input (wait (split-l p) P)
\end{code}
where the \AgdaInductiveConstructor{split-l} constructor indicates that the
thread operates on the most recent channel. In the latter predicate we have

\begin{code}[hide]
  case :
    ∀{Γ Δ A B} (p : Γ ≃ [] + Δ) {P : Process (A ∷ Δ)} {Q : Process (B ∷ Δ)} →
    Input (case (split-l p) P Q)
  join :
    ∀{Γ Δ A B} (p : Γ ≃ [] + Δ) {P : Process (B ∷ A ∷ Δ)} →
    Input (join (split-l p) P)

data Client where
  client :
    ∀{Γ Δ A} (p : Γ ≃ [] + Δ)
    {P : Process (A ∷ Δ)} →
    Client (client (split-l p) P)
  weaken :
    ∀{Γ Δ A} (p : Γ ≃ [] + Δ)
    {P : Process Δ} →
    Client (weaken {A = A} (split-l p) P)
  contract :
    ∀{Γ Δ A} (p : Γ ≃ [] + Δ)
    {P : Process (¿ A ∷ ¿ A ∷ Δ)} →
    Client (contract (split-l p) P)

data Output where
  close : Output close
  select :
    ∀{Γ Δ A B} (x : Bool) (p : Γ ≃ [] + Δ) {P : Process ((if x then A else B) ∷ Δ)} →
    Output (select x (split-l p) P)
  fork :
    ∀{Γ Δ Δ₁ Δ₂ A B} (p : Γ ≃ [] + Δ) (q : Δ ≃ Δ₁ + Δ₂)
    {P : Process (A ∷ Δ₁)} {Q : Process (B ∷ Δ₂)} →
    Output (fork (split-l p) q P Q)

data Delayed where
  fail :
    ∀{A Γ Δ}
    (p : Γ ≃ ⊤ , Δ) → Delayed (fail (split-r {A} p))
\end{code}

\begin{code}
  wait : ∀{C Γ Δ} (p : Γ ≃ ⊥ , Δ) {P : Process (C ∷ Δ)} →
         Delayed (wait (split-r p) P)
\end{code}
where the \AgdaInductiveConstructor{split-r} constructor indicates that the
thread operates on a channel other than the most recent one.

\begin{code}[hide]
  case :
    ∀{Γ Δ C A B} (p : Γ ≃ A & B , Δ) {P : Process (A ∷ C ∷ Δ)} {Q : Process (B ∷ C ∷ Δ)} →
    Delayed (case (split-r p) P Q)
  join :
    ∀{Γ Δ C A B} (p : Γ ≃ A ⅋ B , Δ) {P : Process (B ∷ A ∷ C ∷ Δ)} →
    Delayed (join (split-r p) P)
  select :
    ∀{Γ Δ C A B} (x : Bool) (p : Γ ≃ A ⊕ B , Δ) {P : Process ((if x then A else B) ∷ C ∷ Δ)} →
    Delayed (select x (split-r p) P)
  fork-l :
    ∀{Γ Δ Δ₁ Δ₂ C A B} (p : Γ ≃ A ⊗ B , Δ) (q : Δ ≃ Δ₁ + Δ₂)
    {P : Process (A ∷ C ∷ Δ₁)} {Q : Process (B ∷ Δ₂)} →
    Delayed (fork (split-r p) (split-l q) P Q)
  fork-r :
    ∀{Γ Δ Δ₁ Δ₂ C A B} (p : Γ ≃ A ⊗ B , Δ) (q : Δ ≃ Δ₁ + Δ₂)
    {P : Process (A ∷ Δ₁)} {Q : Process (B ∷ C ∷ Δ₂)} →
    Delayed (fork (split-r p) (split-r q) P Q)
  client :
    ∀{Γ Δ A C} (p : Γ ≃ ¿ A , Δ) {P : Process (A ∷ C ∷ Δ)} →
    Delayed (client (split-r p) P)
  weaken :
    ∀{Γ Δ A C} (p : Γ ≃ ¿ A , Δ) {P : Process (C ∷ Δ)} →
    Delayed (weaken (split-r p) P)
  contract :
    ∀{Γ Δ A C} (p : Γ ≃ ¿ A , Δ) {P : Process (¿ A ∷ ¿ A ∷ C ∷ Δ)} →
    Delayed (contract (split-r p) P)

data Server where
  server :
    ∀{Γ Δ A} (p : Γ ≃ [] + Δ) (un : Un Δ) {P : Process (A ∷ Δ)} →
    Server (server (split-l p) un P)

data DelayedServer where
  server :
    ∀{Γ Δ A C} (p : Γ ≃ ¡ A , Δ) (un : Un Δ) {P : Process (A ∷ ¿ C ∷ Δ)} →
    DelayedServer (server (split-r p) (un-∷ un) P)
\end{code}
\end{AgdaAlign}

@@

\begin{code}[hide]
link-thread : ∀{Γ A B} (d : Dual A B) (p : Γ ≃ [ A ] + [ B ]) → Thread (link d p)
link-thread d p = inj₁ (link d p)

@@

wait-thread : ∀{Γ Δ} (p : Γ ≃ [ ⊥ ] + Δ) {P : Process Δ} → Thread (wait p P)
wait-thread (split-l p) = inj₂ (inj₂ (inj₂ (inj₁ (wait p))))
wait-thread (split-r p) = inj₂ (inj₁ (wait p))

fail-thread : ∀{Γ Δ} (p : Γ ≃ [ ⊤ ] + Δ) → Thread (fail p)
fail-thread (split-l p) = inj₂ (inj₂ (inj₂ (inj₁ (fail p))))
fail-thread (split-r p) = inj₂ (inj₁ (fail p))

case-thread :
  ∀{Γ Δ A B} (p : Γ ≃ [ A & B ] + Δ) {P : Process (A ∷ Δ)} {Q : Process (B ∷ Δ)} →
  Thread (case p P Q)
case-thread (split-l p) = inj₂ (inj₂ (inj₂ (inj₁ (case p))))
case-thread (split-r p) = inj₂ (inj₁ (case p))

join-thread :
  ∀{Γ Δ A B} (p : Γ ≃ [ A ⅋ B ] + Δ) {P : Process (B ∷ A ∷ Δ)} →
  Thread (join p P)
join-thread (split-l p) = inj₂ (inj₂ (inj₂ (inj₁ (join p))))
join-thread (split-r p) = inj₂ (inj₁ (join p))

select-thread :
  ∀{Γ Δ A B} (x : Bool) (p : Γ ≃ A ⊕ B , Δ) {P : Process ((if x then A else B) ∷ Δ)} →
  Thread (select x p P)
select-thread x (split-l p) = inj₂ (inj₂ (inj₁ (select x p)))
select-thread x (split-r p) = inj₂ (inj₁ (select x p))

fork-thread :
  ∀{Γ Δ Δ₁ Δ₂ A B} (p : Γ ≃ [ A ⊗ B ] + Δ) (q : Δ ≃ Δ₁ + Δ₂)
  {P : Process (A ∷ Δ₁)} {Q : Process (B ∷ Δ₂)} →
  Thread (fork p q P Q)
fork-thread (split-l p) q = inj₂ (inj₂ (inj₁ (fork p q)))
fork-thread (split-r p) (split-l q) = inj₂ (inj₁ (fork-l p q))
fork-thread (split-r p) (split-r q) = inj₂ (inj₁ (fork-r p q))

client-thread :
  ∀{Γ Δ A} (p : Γ ≃ [ ¿ A ] + Δ)
  {P : Process (A ∷ Δ)} →
  Thread (client p P)
client-thread (split-l p) = inj₂ (inj₂ (inj₂ (inj₂ (inj₁ (client p)))))
client-thread (split-r p) = inj₂ (inj₁ (client p))

weaken-thread :
  ∀{Γ Δ A} (p : Γ ≃ [ ¿ A ] + Δ)
  {P : Process Δ} →
  Thread (weaken {A = A} p P)
weaken-thread (split-l p) = inj₂ (inj₂ (inj₂ (inj₂ (inj₁ (weaken p)))))
weaken-thread (split-r p) = inj₂ (inj₁ (weaken p))

contract-thread :
  ∀{Γ Δ A} (p : Γ ≃ [ ¿ A ] + Δ)
  {P : Process (¿ A ∷ ¿ A ∷ Δ)} →
  Thread (contract p P)
contract-thread (split-l p) = inj₂ (inj₂ (inj₂ (inj₂ (inj₁ (contract p)))))
contract-thread (split-r p) = inj₂ (inj₁ (contract p))

server-thread :
  ∀{Γ Δ A} (p : Γ ≃ [ ¡ A ] + Δ) (un : Un Δ) {P : Process (A ∷ Δ)} →
  Thread (server p un P)
server-thread (split-l p) un = inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ (server p un))))))
server-thread (split-r p) (un-∷ un) = inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (server p un))))))
\end{code}

@@

\begin{code}
data CanonicalCut {Γ} : Process Γ → Set where
  cc-link :
    ∀{Γ₁ Γ₂ A B} (d : Dual A B) (p : Γ ≃ Γ₁ + Γ₂)
    {P : Process (A ∷ Γ₁)} {Q : Process (B ∷ Γ₂)} →
    Link P → CanonicalCut (cut d p P Q)
  cc-delayed :
    ∀{Γ₁ Γ₂ A B} (d : Dual A B) (p : Γ ≃ Γ₁ + Γ₂)
    {P : Process (A ∷ Γ₁)} {Q : Process (B ∷ Γ₂)} →
    Delayed P → CanonicalCut (cut d p P Q)
  cc-delayed-server :
    ∀{Γ₁ Γ₂ A B} (d : Dual A B) (p : Γ ≃ Γ₁ + Γ₂)
    {P : Process (A ∷ Γ₁)} {Q : Process (B ∷ Γ₂)} →
    DelayedServer P → Server Q → CanonicalCut (cut d p P Q)
  cc-redex :
    ∀{Γ₁ Γ₂ A B} (d : Dual A B) (p : Γ ≃ Γ₁ + Γ₂)
    {P : Process (A ∷ Γ₁)} {Q : Process (B ∷ Γ₂)} →
    Output P → Input Q → CanonicalCut (cut d p P Q)
  cc-connect :
    ∀{Γ₁ Γ₂ A B} (d : Dual A B) (p : Γ ≃ Γ₁ + Γ₂)
    {P : Process (A ∷ Γ₁)} {Q : Process (B ∷ Γ₂)} →
    Server P → Client Q → CanonicalCut (cut d p P Q)
\end{code}

@@

\begin{code}[hide]
output-output :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Output P × Output Q)
output-output d-𝟙-⊥ (close , ())

output-client :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Output P × Client Q)
output-client () (close , client p)

output-server :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Output P × Server Q)
output-server () (close , server p un)

output-delayed-server :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Output P × DelayedServer Q)
output-delayed-server () (close , server p un)

input-input :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Input P × Input Q)
input-input d-⊤-𝟘 (fail p , ())

input-client :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Input P × Client Q)
input-client () (fail p₁ , client p)

input-server :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Input P × Server Q)
input-server () (fail p₁ , server p un)

input-delayed-server :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Input P × DelayedServer Q)
input-delayed-server () (fail p₁ , server p un)

client-client :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Client P × Client Q)
client-client () (client p , client p₁)

client-delayed-server :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Client P × DelayedServer Q)
client-delayed-server () (client p₁ , server p un)

server-server :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (Server P × Server Q)
server-server () (server p un , server p₁ un₁)

delayed-server-delayed-served :
  ∀{Γ Δ A B} {P : Process (A ∷ Γ)} {Q : Process (B ∷ Δ)} → Dual A B → ¬ (DelayedServer P × DelayedServer Q)
delayed-server-delayed-served () (server p un , server p₁ un₁)
\end{code}

@@

\begin{code}
canonical-cut :
  ∀{Γ Γ₁ Γ₂ A B} {P : Process (A ∷ Γ₁)} {Q : Process (B ∷ Γ₂)}
  (d : Dual A B) (p : Γ ≃ Γ₁ + Γ₂) →
  Thread P → Thread Q → ∃[ R ] CanonicalCut R × cut d p P Q ⊒ R
\end{code}

>>>>

\begin{code}[hide]
{-# OPTIONS --rewriting #-}
open import Data.Sum
open import Data.Product using (_×_; _,_; ∃; ∃-syntax)
open import Data.List.Base using ([]; _∷_; [_])
open import Relation.Nullary using (¬_; contradiction)
open import Relation.Binary.PropositionalEquality using (refl)

@@

\begin{AgdaAlign}
\begin{code}[hide]
data Cut where
  cut : ∀{Γ Γ₁ Γ₂ A P Q} (p : Γ ≃ Γ₁ + Γ₂) -> Cut (cut {A} p P Q)

data Link where
  link : ∀{Γ A} (p : Γ ≃ [ A ] + [ dual A ]) → Link (link p)

data Input where
  fail : ∀{Γ Δ} (p : Γ ≃ [] + Δ) → Input (fail (< p))
\end{code}

\begin{code}
  wait : ∀{Γ Δ P} (p : Γ ≃ [] + Δ) → Input (wait (< p) P)
\end{code}
where the \AgdaInductiveConstructor{split-l} constructor indicates that the
thread operates on the most recent channel. In the latter predicate we have

\begin{code}[hide]
  case : ∀{Γ Δ A B P Q} (p : Γ ≃ [] + Δ) → Input (case {A} {B} (< p) P Q)
  join : ∀{Γ Δ A B P} (p : Γ ≃ [] + Δ) → Input (join {A} {B} (< p) P)
  all  : ∀{A Γ Δ F} (p : Γ ≃ [] + Δ) -> Input (all {A} (< p) F)

data Output where
  close  : Output close
  left   : ∀{Γ Δ A B P} (p : Γ ≃ [] + Δ) → Output (left {A} {B} (< p) P)
  right  : ∀{Γ Δ A B P} (p : Γ ≃ [] + Δ) → Output (right {A} {B} (< p) P)
  fork   : ∀{Γ Δ Δ₁ Δ₂ A B P Q} (p : Γ ≃ [] + Δ) (q : Δ ≃ Δ₁ + Δ₂) -> Output (fork {A} {B} (< p) q P Q)
  ex     : ∀{A B Γ Δ P} (p : Γ ≃ [] + Δ) -> Output (ex {A} {B} (< p) P)

data Delayed where
  fail     : ∀{C Γ Δ} (p : Γ ∋ ⊤ ⊳ Δ) → Delayed (fail (>_ {C} p))
\end{code}

\begin{code}
  wait     : ∀{C Γ Δ P} (p : Γ ∋ ⊥ ⊳ Δ) → Delayed (wait (>_ {C} p) P)
\end{code}
where the \AgdaInductiveConstructor{split-r} constructor indicates that the
thread operates on a channel other than the most recent one.

\begin{code}[hide]
  case     : ∀{Γ Δ C A B P Q} (p : Γ ∋ A & B ⊳ Δ) → Delayed (case {A} {B} (>_ {C} p) P Q)
  join     : ∀{Γ Δ C A B P} (p : Γ ∋ A ⅋ B ⊳ Δ) → Delayed (join (>_ {C} p) P)
  left     : ∀{Γ Δ C A B P} (p : Γ ∋ A ⊕ B ⊳ Δ) → Delayed (left (>_ {C} p) P)
  right    : ∀{Γ Δ C A B P} (p : Γ ∋ A ⊕ B ⊳ Δ) → Delayed (right (>_ {C} p) P)
  fork-l   : ∀{Γ Δ Δ₁ Δ₂ C A B P Q} (p : Γ ∋ A ⊗ B ⊳ Δ) (q : Δ ≃ Δ₁ + Δ₂) →
             Delayed (fork (>_ {C} p) (< q) P Q)
  fork-r   : ∀{Γ Δ Δ₁ Δ₂ C A B P Q} (p : Γ ∋ A ⊗ B ⊳ Δ) (q : Δ ≃ Δ₁ + Δ₂) →
             Delayed (fork (>_ {C} p) (> q) P Q)
  client   : ∀{Γ Δ A C P} (p : Γ ∋ `? A ⊳ Δ) → Delayed (client (>_ {C} p) P)
  weaken   : ∀{Γ Δ A C P} (p : Γ ∋ `? A ⊳ Δ) → Delayed (weaken (>_ {C} p) P)
  contract : ∀{Γ Δ A C P} (p : Γ ∋ `? A ⊳ Δ) → Delayed (contract (>_ {C} p) P)
  ex       : ∀{A B C Γ Δ P} (p : Γ ∋ `∃ A ⊳ Δ) → Delayed (ex {A} {B} (>_ {C} p) P)
  all      : ∀{A C Γ Δ F} (p : Γ ∋ `∀ A ⊳ Δ) → Delayed (all (>_ {C} p) F)

data Client where
  client   : ∀{Γ Δ A P} (p : Γ ≃ [] + Δ) → Client (client {A} (< p) P)
  weaken   : ∀{Γ Δ A P} (p : Γ ≃ [] + Δ) → Client (weaken {A} (< p) P)
  contract : ∀{Γ Δ A P} (p : Γ ≃ [] + Δ) → Client (contract {A} (< p) P)

data Server where
  server : ∀{Γ Δ A P} (p : Γ ≃ [] + Δ) (un : Un Δ) → Server (server {A} (< p) un P)

data DelayedServer where
  server : ∀{Γ Δ A C P} (p : Γ ∋ `! A ⊳ Δ) (un : Un Δ) →
           DelayedServer (server (> p) (un-∷ {C} un) P)
\end{code}
\end{AgdaAlign}

@@

\begin{code}[hide]
link-thread : ∀{A Γ} (p : Γ ≃ [ A ] + [ dual A ]) → Thread (link p)
link-thread p = inj₁ (link p)

@@

wait-thread : ∀{Γ Δ P} (p : Γ ≃ [ ⊥ ] + Δ) → Thread (wait p P)
wait-thread (< p) = inj₂ (inj₂ (inj₂ (inj₁ (wait p))))
wait-thread (> p) = inj₂ (inj₁ (wait p))

fail-thread : ∀{Γ Δ} (p : Γ ≃ [ ⊤ ] + Δ) → Thread (fail p)
fail-thread (< p) = inj₂ (inj₂ (inj₂ (inj₁ (fail p))))
fail-thread (> p) = inj₂ (inj₁ (fail p))

case-thread : ∀{A B Γ Δ P Q} (p : Γ ≃ [ A & B ] + Δ) → Thread (case p P Q)
case-thread (< p) = inj₂ (inj₂ (inj₂ (inj₁ (case p))))
case-thread (> p) = inj₂ (inj₁ (case p))

join-thread : ∀{A B Γ Δ P} (p : Γ ≃ [ A ⅋ B ] + Δ) → Thread (join p P)
join-thread (< p) = inj₂ (inj₂ (inj₂ (inj₁ (join p))))
join-thread (> p) = inj₂ (inj₁ (join p))

left-thread : ∀{A B Γ Δ P} (p : Γ ∋ A ⊕ B ⊳ Δ) → Thread (left p P)
left-thread (< p) = inj₂ (inj₂ (inj₁ (left p)))
left-thread (> p) = inj₂ (inj₁ (left p))

right-thread : ∀{A B Γ Δ P} (p : Γ ∋ A ⊕ B ⊳ Δ) → Thread (right p P)
right-thread (< p) = inj₂ (inj₂ (inj₁ (right p)))
right-thread (> p) = inj₂ (inj₁ (right p))

fork-thread : ∀{A B Γ Δ Δ₁ Δ₂ P Q} (p : Γ ≃ [ A ⊗ B ] + Δ) (q : Δ ≃ Δ₁ + Δ₂) → Thread (fork p q P Q)
fork-thread (< p) q = inj₂ (inj₂ (inj₁ (fork p q)))
fork-thread (> p) (< q) = inj₂ (inj₁ (fork-l p q))
fork-thread (> p) (> q) = inj₂ (inj₁ (fork-r p q))

client-thread : ∀{A Γ Δ P} (p : Γ ≃ [ `? A ] + Δ) → Thread (client p P)
client-thread (< p) = inj₂ (inj₂ (inj₂ (inj₂ (inj₁ (client p)))))
client-thread (> p) = inj₂ (inj₁ (client p))

weaken-thread : ∀{A Γ Δ P} (p : Γ ≃ [ `? A ] + Δ) → Thread (weaken {A = A} p P)
weaken-thread (< p) = inj₂ (inj₂ (inj₂ (inj₂ (inj₁ (weaken p)))))
weaken-thread (> p) = inj₂ (inj₁ (weaken p))

contract-thread : ∀{A Γ Δ P} (p : Γ ≃ [ `? A ] + Δ) → Thread (contract p P)
contract-thread (< p) = inj₂ (inj₂ (inj₂ (inj₂ (inj₁ (contract p)))))
contract-thread (> p) = inj₂ (inj₁ (contract p))

server-thread : ∀{A Γ Δ P} (p : Γ ≃ [ `! A ] + Δ) (un : Un Δ) → Thread (server p un P)
server-thread (< p) un = inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ (server p un))))))
server-thread (> p) (un-∷ un) = inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (server p un))))))

ex-thread : ∀{A B Γ Δ P} (p : Γ ∋ `∃ A ⊳ Δ) -> Thread (ex {A} {B} p P)
ex-thread (< p) = inj₂ (inj₂ (inj₁ (ex p)))
ex-thread (> p) = inj₂ (inj₁ (ex p))

all-thread : ∀{A Γ Δ F} (p : Γ ∋ `∀ A ⊳ Δ) -> Thread (all p F)
all-thread (< p) = inj₂ (inj₂ (inj₂ (inj₁ (all p))))
all-thread (> p) = inj₂ (inj₁ (all p))
\end{code}

@@

\begin{code}
data CanonicalCut {Γ} : Process Γ → Set where
  cc-link           : ∀{Γ₁ Γ₂ A P Q} (p : Γ ≃ Γ₁ + Γ₂) →
                      Link P → CanonicalCut (cut {A} p P Q)
  cc-delayed        : ∀{Γ₁ Γ₂ A P Q} (p : Γ ≃ Γ₁ + Γ₂) →
                      Delayed P → CanonicalCut (cut {A} p P Q)
  cc-delayed-server : ∀{Γ₁ Γ₂ A P Q} (p : Γ ≃ Γ₁ + Γ₂) →
                      DelayedServer P → Server Q → CanonicalCut (cut {A} p P Q)
  cc-redex          : ∀{Γ₁ Γ₂ A P Q} (p : Γ ≃ Γ₁ + Γ₂) →
                      Output P → Input Q → CanonicalCut (cut {A} p P Q)
  cc-connect        : ∀{Γ₁ Γ₂ A P Q} (p : Γ ≃ Γ₁ + Γ₂) →
                      Server P → Client Q → CanonicalCut (cut {A} p P Q)
\end{code}

@@

\begin{code}[hide]
output-output : ∀{A Γ Δ P Q} → ¬ (Output {A ∷ Γ} P × Output {dual A ∷ Δ} Q)
output-output (close , ())

output-client : ∀{A Γ Δ P Q} → ¬ (Output {A ∷ Γ} P × Client {dual A ∷ Δ} Q)
output-client (close , ())

output-server : ∀{A Γ Δ P Q} → ¬ (Output {A ∷ Γ} P × Server {dual A ∷ Δ} Q)
output-server (close , ())

output-delayed-server : ∀{A Γ Δ P Q} → ¬ (Output {A ∷ Γ} P × DelayedServer {dual A ∷ Δ} Q)
output-delayed-server (close , ())

input-input : ∀{A Γ Δ P Q} → ¬ (Input {A ∷ Γ} P × Input {dual A ∷ Δ} Q)
input-input (fail _ , ())

input-client : ∀{A Γ Δ P Q} → ¬ (Input {A ∷ Γ} P × Client {dual A ∷ Δ} Q)
input-client (fail _ , ())

input-server : ∀{A Γ Δ P Q} → ¬ (Input {A ∷ Γ} P × Server {dual A ∷ Δ} Q)
input-server (fail _ , ())

input-delayed-server : ∀{A Γ Δ P Q} → ¬ (Input {A ∷ Γ} P × DelayedServer {dual A ∷ Δ} Q)
input-delayed-server (fail _ , ())

client-client : ∀{A Γ Δ P Q} → ¬ (Client {A ∷ Γ} P × Client {dual A ∷ Δ} Q)
client-client (client _ , ())

client-delayed-server : ∀{A Γ Δ P Q} → ¬ (Client {A ∷ Γ} P × DelayedServer {dual A ∷ Δ} Q)
client-delayed-server (client _ , ())

server-server : ∀{A Γ Δ P Q} → ¬ (Server {A ∷ Γ} P × Server {dual A ∷ Δ} Q)
server-server (server _ _ , ())

delayed-server-delayed-served : ∀{A Γ Δ P Q} → ¬ (DelayedServer {A ∷ Γ} P × DelayedServer {dual A ∷ Δ} Q)
delayed-server-delayed-served (server _ _ , ())
\end{code}

@@

\begin{code}
canonical-cut : ∀{A Γ Γ₁ Γ₂ P Q} (p : Γ ≃ Γ₁ + Γ₂) →
                Thread P → Thread Q → ∃[ R ] CanonicalCut R × cut {A} p P Q ⊒ R
\end{code}

\begin{code}[hide]
canonical-cut pc (inj₁ x) Qt = _ , cc-link pc x , s-refl
canonical-cut pc (inj₂ x) (inj₁ y) = _ , cc-link (+-comm pc) y , s-comm pc
canonical-cut pc (inj₂ (inj₁ x)) (inj₂ y) = _ , cc-delayed pc x , s-refl
canonical-cut pc (inj₂ (inj₂ x)) (inj₂ (inj₁ y)) = _ , cc-delayed (+-comm pc) y , s-comm pc
canonical-cut pc (inj₂ (inj₂ (inj₁ x))) (inj₂ (inj₂ (inj₁ y))) = contradiction (x , y) output-output
canonical-cut pc (inj₂ (inj₂ (inj₁ x))) (inj₂ (inj₂ (inj₂ (inj₁ y)))) = _ , cc-redex pc x y , s-refl
canonical-cut pc (inj₂ (inj₂ (inj₁ x))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ y))))) = contradiction (x , y) output-client
canonical-cut pc (inj₂ (inj₂ (inj₁ x))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ y)))))) = contradiction (x , y) output-server
canonical-cut pc (inj₂ (inj₂ (inj₁ x))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ y)))))) = contradiction (x , y) output-delayed-server
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₁ x)))) (inj₂ (inj₂ (inj₁ y))) = _ , cc-redex (+-comm pc) y x , s-comm pc
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ x))))) (inj₂ (inj₂ (inj₁ y))) = contradiction (y , x) output-client
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ x)))))) (inj₂ (inj₂ (inj₁ y))) = contradiction (y , x) output-server
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ x)))))) (inj₂ (inj₂ (inj₁ y))) = contradiction (y , x) output-delayed-server
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₁ x)))) (inj₂ (inj₂ (inj₂ (inj₁ y)))) = contradiction (x , y) (input-input)
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₁ x)))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ y))))) = contradiction (x , y) input-client
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₁ x)))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ y)))))) = contradiction (x , y) input-server
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₁ x)))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ y)))))) = contradiction (x , y) input-delayed-server
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ x))))) (inj₂ (inj₂ (inj₂ (inj₁ y)))) = contradiction (y , x) input-client
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ x)))))) (inj₂ (inj₂ (inj₂ (inj₁ y)))) = contradiction (y , x) input-server
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ x)))))) (inj₂ (inj₂ (inj₂ (inj₁ y)))) = contradiction (y , x) input-delayed-server
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ x))))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ y))))) = contradiction (x , y) client-client
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ x))))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ y)))))) = _ , cc-connect (+-comm pc) y x , s-comm pc
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ x))))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ y)))))) = contradiction (x , y) client-delayed-server
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ x)))))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ y))))) = _ , cc-connect pc x y , s-refl
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ x)))))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ y))))) = contradiction (y , x) client-delayed-server
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ x)))))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ y)))))) = contradiction (x , y) server-server
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ x)))))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ y)))))) = _ , cc-delayed-server (+-comm pc) y x , s-comm pc
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ x)))))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₁ y)))))) = _ , cc-delayed-server pc x y , s-refl
canonical-cut pc (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ x)))))) (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ (inj₂ y)))))) = contradiction (x , y) delayed-server-delayed-served
